Using Visual Analytics to Explain\\[1ex] Black-Box Machine Learning

### 2018-04-02 tex/summary.tex
bug fixes

Interestingly, because humans are used to having contextual knowledge about real world problems machine learning is trying to solve, it often seems surprising when and why a model failed, since the correct prediction ``is so obvious".
This also means, that repeatedly seeing that a model performs correctly, especially when providing a reasoning behind the decision in the form of \emph{explanations} might lead to overconfidence of the human in the capabilities of the model.
\todo{explanations considered harmful?}
\todo{TODO}
* automl and the human role in ML
* vis systems from last year
* attention models
* additive models

>>>>

Interestingly, because humans are used to having contextual knowledge about real world problems machine learning is trying to solve, it often seems surprising when and why a model failed, since the correct prediction ``is so obvious".
This also means, that repeatedly seeing that a model performs correctly, especially when providing a reasoning behind the decision in the form of \emph{explanations} might lead to overconfidence of the human in the capabilities of the model~\cite{harmful}.
\todo{TODO}
* automl and the human role in ML
* vis systems from last year
* attention models
* additive models
